For Induction-Induction, Induction is Enough

### 2019-11-12 paper/paper.tex
mathsf font for _^D constructors in the intro

The elimination principle for the above IIT has two motives and one method
for each constructor. It is an example of a \emph{recursive-recursive}
function (following the nomenclature of \cite{forsberg-phd}) which
means that there are two mutually defined functions, where the type of
the second function depends on the first function. The proof assistant
Agda \cite{norell07thesis} allows the definition of such functions
(even from non-IITs) and it is also currently the only proof assistant
supporting IITs\footnote{An experimental version of Coq with IITs is also
  available on github.}. The elimination principle for $\Con$--$\Ty$ says that
given the following components,
\begin{alignat*}{5}
  & Con^D && : \Con\ra\Set \\
  & Ty^D && : Con^D\,\Gamma\ra\Ty\,\Gamma\ra\Set \\
  & empty^D && : Con^D\,\mathsf{empty} \\
  & ext^D && : (\Gamma^D:Con^D\,\Gamma)\ra Ty^D\,\Gamma^D\,A\ra Con^D\,(\mathsf{ext}\,\Gamma\,A) \\
  & U^D && : (\Gamma^D:Con^D\,\Gamma)\ra Ty^D\,\Gamma^D\,(\mathsf{U}\,\Gamma) \\
  & El^D && : (\Gamma^D:Con^D\,\Gamma)\ra\,Ty^D\,(ext^D\,\Gamma^D\,(U^D\,\Gamma^D))\,(\mathsf{El}\,\Gamma)
%  & Pi^D && : (\Gamma^D:Con^D\,\Gamma)(A^D:Ty^D\,\Gamma^D\,A)\ra Ty^D\,(ext^D\,\Gamma^D\,A^D)\ra\,Ty^D\,\Gamma^D\,(\mathsf{Pi}\,\Gamma\,A\,B)
\end{alignat*}
we obtain two functions
\begin{alignat*}{5}
  & \mathsf{elimCon} && : (\Gamma:\Con)\ra Con^D\,\Gamma \\
  & \mathsf{elimTy} && : (A:\Ty\,\Gamma)\ra Ty^D\,(\mathsf{elimCon}\,\Gamma)
\end{alignat*}
with the following computation rules.
\begin{alignat*}{5}
  & \mathsf{elimCon}\,\mathsf{empty} && = empty^D \\
  & \mathsf{elimCon}\,(\mathsf{ext}\,\Gamma\,A) && = ext^D\,(\mathsf{elimCon}\,\Gamma)\,(\mathsf{elimTy}\,A) \\
  & \mathsf{elimTy}\,(\mathsf{U}\,\Gamma) && = U^D\,(\mathsf{elimCon}\,\Gamma) \\
  & \mathsf{elimTy}\,(\mathsf{El}\,\Gamma) && = El^D\,(\mathsf{elimCon}\,\Gamma)
\end{alignat*}

>>>>

The elimination principle for the above IIT has two motives and one method
for each constructor. It is an example of a \emph{recursive-recursive}
function (following the nomenclature of \cite{forsberg-phd}) which
means that there are two mutually defined functions, where the type of
the second function depends on the first function. The proof assistant
Agda \cite{norell07thesis} allows the definition of such functions
(even from non-IITs) and it is also currently the only proof assistant
supporting IITs\footnote{An experimental version of Coq with IITs is also
  available on github.}. The elimination principle for $\Con$--$\Ty$ says that
given the following components,
\begin{alignat*}{5}
  & \Con^D && : \Con\ra\Set \\
  & \Ty^D && : \Con^D\,\Gamma\ra\Ty\,\Gamma\ra\Set \\
  & \mathsf{empty}^D && : \Con^D\,\mathsf{empty} \\
  & \mathsf{ext}^D && : (\Gamma^D:\Con^D\,\Gamma)\ra \Ty^D\,\Gamma^D\,A\ra \Con^D\,(\mathsf{ext}\,\Gamma\,A) \\
  & \U^D && : (\Gamma^D:\Con^D\,\Gamma)\ra \Ty^D\,\Gamma^D\,(\mathsf{U}\,\Gamma) \\
  & \El^D && : (\Gamma^D:\Con^D\,\Gamma)\ra\,\Ty^D\,(\mathsf{ext}^D\,\Gamma^D\,(\U^D\,\Gamma^D))\,(\mathsf{El}\,\Gamma)
%  & Pi^D && : (\Gamma^D:\Con^D\,\Gamma)(A^D:\Ty^D\,\Gamma^D\,A)\ra \Ty^D\,(\mathsf{ext}^D\,\Gamma^D\,A^D)\ra\,\Ty^D\,\Gamma^D\,(\mathsf{Pi}\,\Gamma\,A\,B)
\end{alignat*}
we obtain two functions
\begin{alignat*}{5}
  & \mathsf{elimCon} && : (\Gamma:\Con)\ra \Con^D\,\Gamma \\
  & \mathsf{elimTy} && : (A:\Ty\,\Gamma)\ra \Ty^D\,(\mathsf{elimCon}\,\Gamma)
\end{alignat*}
with the following computation rules.
\begin{alignat*}{5}
  & \mathsf{elimCon}\,\mathsf{empty} && = \mathsf{empty}^D \\
  & \mathsf{elimCon}\,(\mathsf{ext}\,\Gamma\,A) && = \mathsf{ext}^D\,(\mathsf{elimCon}\,\Gamma)\,(\mathsf{elimTy}\,A) \\
  & \mathsf{elimTy}\,(\mathsf{U}\,\Gamma) && = \U^D\,(\mathsf{elimCon}\,\Gamma) \\
  & \mathsf{elimTy}\,(\mathsf{El}\,\Gamma) && = \El^D\,(\mathsf{elimCon}\,\Gamma)
\end{alignat*}
